### 2020-03-04 doc/icfp20/harmony.tex

In Haskell this would be easy---there is an \texttt{Eq} typeclass and a
method for automatically generating equalities. In the Agda Standard
Library~\citep{agda-stdlib} is a relation with a constructive proof of
membership, and requires far more effort than we need. Alternatives
include defining decidable equality for triads (which requires writing
out 49 cases) or mapping to natural numbers and using already
implemented decidable or boolean equality for those. For now we simply
write the inverse function manually, excluding the rare cases.

>>>>

In Haskell this would be easy---there is an \texttt{Eq} typeclass and a
method for automatically generating equalities. In the Agda Standard
Library~\citep{agda-stdlib} list membership is a relation with
constructive evidence of membership, and requires far more effort we
would like given that we currently don't need to do
proofs. Alternatives include defining decidable equality for triads
(which requires writing out 49 cases) or mapping to natural numbers
and using already implemented decidable or boolean equality for
those. For now we simply write the inverse function manually,
excluding the rare cases.
